\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\usepackage[vietnamese,english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\geometry{margin=1in}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{NGUYEN ANH}}\\
    Backend Developer (Golang \& Python)\\
    \href{mailto:erisanh.dev@gmail.com}{erisanh.dev@gmail.com} \quad
    +84 815 837 673 \quad
    \href{https://github.com/erisanh}{github.com/erisanh}
\end{center}

\section*{Professional Summary}
Backend Developer with over 2 years of experience designing and building scalable, high-performance systems using Golang and Python.
Experienced in RESTful API development, Clean Architecture, concurrency patterns, transaction management, and third-party integrations including payment gateways, email services, cloud storage, and external reservation APIs.
Proficient in applying modern architectural patterns (Repository/Service, Dependency Injection, CQRS) in production environments.
Seeking a backend role in a dynamic team environment.

\section*{Technical Skills}

\textbf{Languages:} Golang (primary, 2+ years), Python. \\

\textbf{Golang Stack:} Echo, Gin, GORM, Cobra, Asynq, Gorilla; concurrency (goroutines, channels, sync primitives), pgx. \\

\textbf{Python Stack:} FastAPI, SQLAlchemy. \\

\textbf{Databases:} PostgreSQL (pgx, GORM, PGVector, JSONB, indexing strategy), MySQL, Redis. \\

\textbf{Integrations:} Yoyaku API, SendGrid, Google Cloud Storage, VNPay, PayOS, MISA Invoice, AWS S3, Firebase, Mailgun, Slack/Telegram Bot, FCM, OpenAI API. \\

\textbf{Architecture:} RESTful API, Clean Architecture, Repository/Service Pattern, CQRS, Dependency Injection, Transaction Management (ACID, optimistic/pessimistic locking, deadlock prevention). \\

\textbf{DevOps:} Git/GitHub, Docker, Google Cloud Build (CI/CD). \\

\textbf{Practices:} OOP/SOLID, Design Patterns, API Documentation (Swagger), Code Review, AI-assisted development (Cursor, Copilot, n8n), Database Migration Management.

\section*{Work Experience}

\textbf{Backend Developer (Golang)} --- RikkeiSort, Da Nang \hfill Mar 2025 -- Present
\begin{itemize}[leftmargin=*]
    \item Core developer of a multi-brand restaurant reservation platform serving multiple shop chains;
    architected with Clean Architecture (Domain, Application, Infrastructure layers) and CQRS pattern.
    \item Designed and implemented comprehensive booking management: create, edit, cancel, check-in flows
    with conflict detection, table slot management, optimistic/pessimistic locking, and ACID transaction retry logic.
    \item Built inventory management system with bulk update capabilities, block-time setting, shop off-day import, and promotion/coupon processing.
    \item Integrated Yoyaku external reservation API (table statuses, table overlap settings) and SendGrid email service
    with multi-template HTML mail system supporting Japanese locale.
    \item Implemented QR code generation (go-qrcode) and PDF generation (gofpdf) for booking confirmations.
    \item Managed 17+ versioned database migrations with performance indexing strategy (50+ indexes) on PostgreSQL;
    applied BIGSERIAL primary keys and composite/partial indexes.
    \item Deployed on Google Cloud with Cloud Build CI/CD pipeline; containerized with Docker.
    \item Tech Stack: Golang (Echo, GORM, pgx), PostgreSQL, Google Cloud Storage, SendGrid, Docker, Google Cloud Build.
\end{itemize}

\textbf{Backend Developer (Golang)} --- AllyAI JSC, Da Nang \hfill Oct 2024 -- Feb 2025
\begin{itemize}[leftmargin=*]
    \item Core contributor to TripC (Play Store): developed 200+ RESTful APIs using Golang with Repository/Service pattern and Dependency Injection.
    \item Implemented modular system featuring short-lived content feeds (Reels-like), real-time interactions, promotions, multi-type orders, and payment/invoicing integrations (VNPay, PayOS, MISA).
    \item Designed separate entry points: REST API (Gin), CLI administration (Cobra), and asynchronous workers (Asynq).
    \item Integrated AI capabilities (OpenAI, PGVector embeddings) and third-party services (Firebase, AWS S3, Mailgun, Slack).
\end{itemize}

\textbf{Backend Developer (Python)} --- AllyAI JSC, Da Nang \hfill Oct 2024 -- Feb 2025
\begin{itemize}[leftmargin=*]
    \item Developed backend services for AI Agent projects using Python FastAPI.
    \item Built efficient API endpoints and integrated AI models.
\end{itemize}

\textbf{Backend Developer} --- Tekup JSC, Da Nang \hfill Feb 2024 -- Oct 2024
\begin{itemize}[leftmargin=*]
    \item Built and maintained APIs primarily in Python.
    \item Integrated authentication and external services; optimized database queries.
    \item Participated in Agile processes and code reviews.
\end{itemize}

\textbf{Backend Developer Intern} --- TANAAKK, Da Nang \hfill Aug 2023 -- Dec 2023
\begin{itemize}[leftmargin=*]
    \item Implemented CRUD operations and basic API development using Python.
    \item Supported testing and documentation.
\end{itemize}

\section*{Highlighted Projects}

\textbf{Multi-Brand Restaurant Reservation System} --- RikkeiSort
\begin{itemize}[leftmargin=*]
    \item High-performance booking API for multi-brand restaurant chains with full booking lifecycle management.
    \item Designed Clean Architecture with CQRS, Repository/Service pattern, and Dependency Injection; managed 17+ DB migrations.
    \item Key features: booking conflict resolution, table slot management, inventory bulk updates, shop off-day import, coupon management, email notifications, QR/PDF generation, and Yoyaku API integration.
    \item Tech Stack: Golang (Echo, GORM), PostgreSQL, Google Cloud Storage, SendGrid, Docker, Google Cloud Build.
\end{itemize}

\textbf{TripC -- Travel \& E-commerce Platform with Social Features} --- AllyAI JSC
\begin{itemize}[leftmargin=*]
    \item Engineered backend for promotions, QR bookings, payments, invoicing, and short-lived video feeds.
    \item Integrated AI-driven recommendations and chatbots using PGVector and OpenAI.
    \item Tech Stack: Golang (Gin, Cobra, Asynq), GORM, PostgreSQL, Redis, AWS S3, Firebase, OpenAI, MISA.
\end{itemize}

\textbf{AI Agent Platform} --- AllyAI JSC
\begin{itemize}[leftmargin=*]
    \item Designed scalable backend APIs for intelligent agents.
    \item Tech Stack: Python (FastAPI), PostgreSQL, OpenAI.
\end{itemize}

\textbf{Culinary Passport System} --- AllyAI JSC
\begin{itemize}[leftmargin=*]
    \item Developed photo check-ins, gift redemption, and e-commerce features.
    \item Tech Stack: Golang, PostgreSQL, Firebase Storage.
\end{itemize}

\section*{Education}

\textbf{Bachelor of Software Engineering} --- University of Science and Technology, Da Nang \hfill 2020 -- 2024 \\

Relevant courses: Data Structures, Database Systems, Software Engineering, OOP, Computer Networks.

\section*{Additional Skills}

Strong problem-solving, teamwork, and rapid learning abilities (PGVector, OpenAI, concurrency patterns, distributed systems). \\
Comfortable with remote collaboration, Agile methodology, and AI-enhanced workflows. \\

\textbf{Languages:} English (Technical). \\
\textbf{References:} Available upon request. \\
\textbf{Portfolio:} \href{https://github.com/erisanh}{github.com/erisanh}

\end{document}
